---
title: "Heterogeneity Project - Analyses for Study 1A"
output: html_notebook
---


# Load Data and Packages
```{r}
setwd("~/KZNB")
rnd <- read.csv("randomproject_data_aggregated_161021.csv")
rndt <- rnd

library(nlme)
library(lme4)
library(ggplot2)
library(lmerTest)
theme_set(theme_bw(base_size = 14))
#For Bayesian analysis:
library(brms)
library(car)
#For dotplots
library(Rcmdr)

```

# Recoding Variables
```{r}
# so that one unit (-.5, .5) = duration of study
rndt$trial40 <- (rndt$trials.thisN + 1) 
rndt$trial40c <- (rndt$trial40 - 20)/40

rndt$rt <- rndt$response.rt
rndt$logrt <- log(rndt$response.rt)

rndt$id <- rndt$ID

rndt$valenceE <-recode(rndt$valence, as.factor.result=F, '"negative" = -0.5; "positive" = 0.5')

rndt$rtms <- rndt$rt*1000
rndt$logrt <- log(rndt$rtms)

```

# Subsetting to look only at trials labeled as self-descriptive
```{r}

rndtb2 <- subset(rndt, response.keys == "up")

```

# Individual Plots
```{r}
selfrelplot <- ggplot(data=rndtb2, aes(x=valence, y=logrt)) +
  geom_jitter(aes(color=as.factor(valence)), position = position_jitter(width = .2), size=1.5) +
  labs(title = "Log RT by Valence - Self-Relevant Traits Only", x="id", y="Log RT") +
  stat_summary(aes(group=valence), fun.y = mean, geom="point", colour="black", size=2) +
  stat_summary(fun.data=mean_cl_boot, geom='errorbar', size = .5) +
  scale_color_manual(values=c("orangered3", "green4")) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position='none',
        plot.title = element_text(lineheight=.8, face="bold"),
        axis.title.y = element_text(face="bold", vjust=0.5),
        axis.title.x = element_text(face="bold", vjust=-0.35)) +
  facet_wrap(~id) 
selfrelplot
#ggsave(selfrelplot, file = "selfrelplot_N62_170218.pdf", height = 40/2.54, width = 64/2.54)
```


# MLE Analyses 
```{r}
## Updates - Stricter Exclusion Cutoff 2 ######
rndtb2 <- subset(rndt, response.keys == "up")
rndtb <- subset(rndtb2, rt >= .01 & rt < 1.45) #90th percentile or below
rndtb2$rt.z <- scale(rndtb2$rt)
sort(rndtb2$rt.z)
rndtz <- subset(rndtb2,  rt.z < 3) #within 3 SD of the mean RT

# standard model -- Significant main effect of valence
mle1a <- (lm(logrt~valenceE + trial40c, data = rndtz))
summary(mle1a)
mle1b <- (lm(rtms~valenceE + trial40c, data = rndtz)) #run on raw rt
summary(mle1b)

#random intercept model
mle2a <- (lmer(logrt ~ valenceE + trial40c + (1 | id),  data=rndtz))
summary(mle2a)
mle2b <- (lmer(rtms ~ valenceE + trial40c + (1 | id),  data=rndtz))
summary(mle2b)

#random intercept & slope of valence
mle3a <- (lmer(logrt ~ valenceE + trial40c + (1 + valenceE| id),  data=rndtz))
summary(mle3a)
mle3b <- lmer(rtms ~ valenceE + trial40c + (1 + valenceE| id),  data=rndtz)
summary(mle3b)


#random intercept & slope of valence & random effects of time 
mle4a <-(lmer(logrt ~ valenceE + trial40c + (1 + valenceE + trial40c | id) ,  data=rndtz))
summary(mle4a)
mle4b <-(lmer(rtms ~ valenceE + trial40c + (1 + valenceE + trial40c| id) ,  data=rndtz))
summary(mle4b)

#random intercept & slope of valence & random effects of time and word
mle5a <- (lmer(logrt ~ valenceE + trial40c + (1 + valenceE + trial40c | id) + (1 | word),  data=rndtz))
summary(mle5a)

cnf.fe.mle5a <- confint(mle5a, "theta_") #elements of lower triang RE cov mat
cnf.fe.mle5a <- confint(mle5a, "beta-")  #FEs

mle5b <- (lmer(rtms ~ valenceE + trial40c + (1 + valenceE + trial40c| id) + (1 | word),  data=rndtz))
summary(mle5b)

```

# MLE Dot Plot
```{r}
ranef.mle5b<- -174.426 + ranef(mle5b)$id[,2] #ValencE column

quantile(ranef.mle5b, probs=c(.025, .975))

stripchart(ranef.mle5b, pch=21, bg="red", cex=3.5, lwd=2,
           xlim=c(-500, 150), xlab="Trait Valence Effect (in Milliseconds)", cex.axis=1.5, cex.lab=1.5)
abline(v=c(-408, -161, 32), col = c("red", "black", "red"),
       lwd = 3)

```

# Bayesian Analyses 
```{r}
# standard model -- Significant main effect of valence
bayes1a <- (brm(logrt~valenceE + trial40c, data = rndtz))
summary(bayes1a)
bayes1b <- (brm(rtms~valenceE + trial40c, data = rndtz)) #run on raw rt
summary(bayes1b)

#random intercept model
bayes2a <- (brm(logrt ~ valenceE + trial40c + (1 | id),  data=rndtz))
summary(bayes2a)
bayes2b <- (brm(rtms ~ valenceE + trial40c + (1 | id),  data=rndtz))
summary(bayes2b)


#random intercept & slope of valence
bayes3a <-(brm(logrt ~ valenceE + trial40c + (1 + valenceE| id),  data=rndtz))
summary(bayes3a)
bayes3b <-(brm(rtms ~ valenceE + trial40c + (1 + valenceE| id),  data=rndtz))
summary(bayes3b)


#random intercept & slope of valence & random effects of time 
bayes4a <- (brm(logrt ~ valenceE + trial40c + (1 + valenceE + trial40c | id) ,  data=rndtz))
summary(bayes4a)
bayes4b <- (brm(rtms ~ valenceE + trial40c + (1 + valenceE + trial40c| id) ,  data=rndtz))
summary(bayes4b)


#random intercept & slope of valence & random effects of time and word
bayes5a <- (brm(logrt ~ valenceE + trial40c + (1 + valenceE + trial40c | id) + (1 | word),  data=rndtz))
summary(bayes5a)

bayes5b <- (brm(rtms ~ valenceE + trial40c + (1 + valenceE + trial40c| id) + (1 | word),  data=rndtz))
summary(bayes5b)
```

# Bayesian Dotplot
```{r}
ranef.bayes5b <- -175.21 + ranef(bayes5b)$id[,2]

stripchart(ranef.bayes5b, pch=21, bg="blue", cex=3.5, lwd=2,
           xlim=c(-500, 150), xlab="Trait Valence Effect (in Milliseconds)", cex.axis=1.5, cex.lab=1.5)
abline(v=c(quantile(ranef.bayes5b, probs=.025), quantile(ranef.bayes5b, probs=.5), quantile(ranef.bayes5b, probs=.975)), col = c("blue", "blue", "blue"),
       lty = c("dashed", "solid", "dashed"), lwd = 4)

```

# Dotplot comparing MLE and Bayesian Results
```{r}


quantile(ranef.mle5b, probs=c(.025, .975))
quantile(ranef.bayes5b, probs=c(.025, .975))

x1 <- list("MLE"=ranef.mle5b, "Bayes"=ranef.bayes5b)

stripchart(x1,
 main="Multiple stripchart for comparision \n Gray = Mean and SDs, Colored Lines = Quantiles",
 xlab="Random Effects of Valence on RT",
 ylab="Method",
 col=c("red","blue"),
 pch=16,
 cex = 2, 
 cex.axis = 1.5, 
 cex.lab = 1.5,
 xlim=c(-500, 120)
 )
abline(v=c(quantile(ranef.mle5b, probs=.025), quantile(ranef.mle5b, probs=.5), quantile(ranef.mle5b, probs=.975)), col = c("darkred", "darkred", "darkred"),
       lty = c("dashed", "solid", "dashed"), lwd = 4)

abline(v=c(quantile(ranef.bayes5b, probs=.025), quantile(ranef.bayes5b, probs=.5), quantile(ranef.bayes5b, probs=.975)), col = c("darkblue", "darkblue", "darkblue"),
       lty = c("dashed", "solid", "dashed"), lwd = 4)
abline(v=c((-174.426-2*150.26), -174.426, (-174.426+2*150.26)), col = c("darkgray", "darkgray", "darkgray"),
       lty = c("dashed", "solid", "dashed"), lwd = 4)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
